Algebraic properties of CFT coset construction and Schramm-Loewner evolution

### 2011-10-27 AffineLieAlgebras/SLE/article.tex
IOP JPhys Conference series style applied, Mathematica code added.

\documentclass[12pt]{article}
\usepackage{amssymb}

@@

\theoremstyle{definition} \newtheorem{Def}{Definition}
\newcommand{\tr}{\hat\triangleright} \newcommand{\trc}{\triangleright}
\newcommand{\adk}{a^{\dagger}_{\kappa}} \newcommand{\ak}{a_{\kappa}}
\def\bF{\mbox{$\overline{\cal F}$}} \def\F{\mbox{$\cal F$}}

@@

\title{Algebraic properties of CFT coset construction and Schramm-Loewner evolution}
\author{A A Nazarov$^{1,2}$\\
  {\small $^1$ Theoretical Department, SPb State University}\\
  {\small 198904, Sankt-Petersburg, Russia}\\
  {\small$^{2}$ Chebyshev Laboratory,}\\
  {\small Department of Mathematics and Mechanics, SPb State University}\\
  {\small 199178, Saint-Petersburg, Russia}\\
  {\small email: antonnaz@gmail.com}}

\maketitle

@@

\subsection{Schramm-Loewner evolution}
\label{sec:schr-loewn-evol}
To remind of Schramm-Loewner evolution we first describe simple example.

Consider Ising model on triangular lattice on upper half plane (see Fig. \ref{fig:sle}). We impose following boundary condition: all spins are down on one half of the boundary and all spins are up on another half. Then in any configuration we get an interface delimiting two clusters and connecting zero and infinity.

@@

\bibliography{bibliography}{}
\bibliographystyle{utphys}

>>>>

\documentclass[a4paper]{jpconf}

%\documentclass[12pt]{article}
\usepackage{amssymb}

@@

\theoremstyle{definition} \newtheorem{Def}{Definition}
\newcommand{\adk}{a^{\dagger}_{\kappa}} \newcommand{\ak}{a_{\kappa}}
\def\bF{\mbox{$\overline{\cal F}$}} \def\F{\mbox{$\cal F$}}

@@

\title{Algebraic properties of CFT coset construction and Schramm-Loewner evolution}
\author{A A Nazarov$^{1,2}$}
\address{
  $^1$ Department of High-Energy and Elementary Particle Physics, 
  Faculty of Physics, \\ SPb State University
  198904, Saint-Petersburg, Russia}
\address{
  $^{2}$ Chebyshev Laboratory,
  Faculty of Mathematics and Mechanics, \\ SPb State University
  199178, Saint-Petersburg, Russia}

\ead{antonnaz@gmail.com}

@@

\subsection{Schramm-Loewner evolution}
\label{sec:schr-loewn-evol}
Consider Ising model on triangular lattice on upper half plane (see Fig. \ref{fig:sle}). We impose following boundary condition: all spins are down on one half of the boundary and all spins are up on another half. Then in any spin configuration we get an interface delimiting two clusters and connecting zero and infinity (see Figure \ref{fig:sle}).

@@

\bibliography{bibliography}{}
\bibliographystyle{iopart-num}
